---
title: "pdconvert Markdown File"
author: "Trevor Cone"
date: "4/11/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Percent to Decimal

pdconvert has two functions thus far. PercenttoDedimal and DecimaltoPercent, 

The first on is PercenttoDecimal. If you recieve data that has percentages in its contents you can easily visualize what the decimal would be for said percentage but 
this function allows for change where you can use those percentages as decimals in a mathmatical way. 

This function has one argument "percent" this is a vector that takes out the % sign and changes its type to numeric. Then changes it into decimal form with division of 100. 

```{r PercenttoDecimal}
PercenttoDecimal <- function(percent)
{
  percent <- as.numeric(gsub("%", "", percent))
  decimal <- percent / 100
  return(decimal)
}
```

## Decimal to Percent

On the other hand DecimaltoPercent is to take a decimal and changes that decimal to a percent form. I find that for visualizations decimal form can be a little more difficult to read so this can be useful after analysis and visualization purposes. This multiplies the decimal by 100 and adds the % sign. 

```{r DecimaltoPercent}
DecimaltoPercent <- function(decimal)
{
  percent <- paste(decimal * 100, "%", sep = "")
  return(percent)
}
```
## Create Decimal. If you need to create a percentage for two vecotrs you can use the function CreateDecimal() this takes two parameters and divides the first one by the second and returns the result. This will create a decimal for you 
an example is if you have 2 and 4 and put it into this function it will calculate 2 divided by 4 and result in .5 (which is 50%) and you can take that result and plug it into DecimaltoPercent() to find the percent. 
```{r, CreateDecimal}
createdecimal <- function(x,y)
{
  z <- x / y
  return(z)
}
```


## Some examples

Here I have some tests that run each function to demonstrate what I want the functions to do. 

```{r Tests}
x <- c(0.05, 0.25, 0.5, 0.75, 0.99)
y <- c("5%", "25%", "50%", "75%", "99%")
a <- DecimaltoPercent(x)
b <- PercenttoDecimal(y)

x1 <- c(.08, 1, .5, .88, .00001)
y1 <- c("50%", "125%", ".50%", "7.5%", "9900%")
a1 <- DecimaltoPercent(x1)
b1 <- PercenttoDecimal(y1)
a # Decimal to Percent
b # Percent to Decimal
a1 # Decimal to Percent
b1 # Percent to Decimal

#CreateDecimal Example
# two Vectors
x2 <- c(1, 2, 4, 8, 10)
y2 <- c(2, 4, 5, 10, 11)
createdecimals <- CreateDecimal(x2, y2)
createdecimals # created decimals
DecimaltoPercent(createdecimals) # Plug in into DecimaltoPercent function to create our percents format
```
